upwell_IDX

### 2021-05-16 upwell_IDX.Rmd
update

# Detect event: 
detect_event_custom <- function(df){
  res <- detect_event(df, threshClim2 = df$exceedance, minDuration = 1, coldSpells = T)
  return(res)
}
# Calculate the upwelling event metrics
SACTN_upwell_base <- SACTN_US %>% 
  dplyr::rename(t = date) %>% 
  group_by(site) %>% 
  nest() %>% 
  mutate(clim = purrr::map(data, ts2clm, pctile = 25, climatologyPeriod = c("1993-01-01", "2005-10-19"))) %>%
  dplyr::select(-data) %>% 
  unnest(cols = clim) %>%
  left_join(SACTN_upwell, by = c("site", "t")) %>%
  filter(!is.na(exceedance)) %>%
  group_by(site) %>% 
  nest() %>% 
  dplyr::mutate(exceed = purrr::map(data, detect_event_custom)) %>% 
  dplyr::select(-data)

SACTN_upwell_events <- SACTN_upwell_base %>% 
  unnest() %>%
  filter(row_number() %% 2 == 0) %>%
  unnest()
save(SACTN_upwell_events, file = "Data_coast_angle/SACTN_upwell_events.RData")
# save(SACTN_upwell_events, file = "Data_coast_angle/SACTN_upwell_events.RData")

>>>>

# Detect event: 
detect_event_custom <- function(df){
  res <- detect_event(df, threshClim2 = df$exceedance, minDuration = 1, coldSpells = T)
  return(res)
}
# Calculate the upwelling event metrics
SACTN_US <- SACTN_US %>% 
  filter(year(date) %in% seq(2011, 2016, 1))

SACTN_upwell_base <- SACTN_US %>% 
  dplyr::rename(t = date) %>% 
  group_by(site) %>% 
  nest() %>% 
  mutate(clim = purrr::map(data, ts2clm, pctile = 100, climatologyPeriod = c("2011-01-01", "2016-12-31"))) %>%
  dplyr::select(-data) %>% 
  unnest(cols = clim) %>%
  left_join(SACTN_upwell, by = c("site", "t")) %>%
  filter(!is.na(exceedance)) %>%
  group_by(site) %>% 
  nest() %>% 
  dplyr::mutate(exceed = purrr::map(data, detect_event_custom)) %>% 
  dplyr::select(-data)

SACTN_upwell_events <- SACTN_upwell_base %>% 
  unnest() %>%
  filter(row_number() %% 2 == 0) %>%
  unnest()

number_SACTN <-  SACTN_upwell_events%>% 
  filter(site == "Saldanha Bay")

save(SACTN_upwell_events, file = "SACTN_upwell_events.RData")
# save(SACTN_upwell_events, file = "Data_coast_angle/SACTN_upwell_events.RData")
